---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}
f <- function(x) {
  
 f <- function(x) {
  u = x
  for(i in 1:length(x)){
    if(x[i] == 0)
      u[i] = 0
    else
      u[i] = 1
  }
  if(prod(x) != 0)
    prod(x)/x
  else{
    if(length(x) - sum(u) == 1){
      y = x
      for(i in 1:length(x)){
        if(x[i] != 0)
          y[i] = x[i]
        else
          y[i] = 1
      }
      z = x
      for(i in 1:length(x)){
        if(x[i] != 0)
          z[i] = 0
        else
          z[i] = prod(y)
      }
      z
    }
    else
      if(length(x) - sum(u) > 1){
        z = 0*x
        z
        }
      }
  }
a<- c(1, 5, 2, 8)
f(a)
b<- c(5, 0, 2, 8)
f(b)
c<- c(1, 0, 2, 0)
f(c)


}

```
    


## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers … except for: 
   multiples of 3 = “Fizz” 
   multiples of 5 = “Buzz”. 
   multiples of 3 and 5 = “FizzBuzz”
   
### Example

    > x <- 1:20
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz


### Solution

```{r}
f <- function(x) {
f <- function(x) {
  z = x
  for(i in 1:length(x))
  {
    if(x[i] %% 15 == 0)
      z[i] = 'FizzBuzz'
    else
      {
        if(x[i] %% 3 == 0)
          z[i] = 'Fizz'
        else
        {
          if(x[i] %% 5 == 0)
            z[i] = 'Buzz'
        }
      }
  }
  z
}
x <- 1:30
f(x)
  
}
```
