---
title: "02-exercises"
author: "Christopher Brown"
date: "April 13, 2016"
output: html_document
---

This exercise uses the **Fuel Economy** data set from the **AppliedPredicitiveModeling** package.

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
... = NULL  # Needed for aesthetics 

```



## Exercise 1

Hint: See `?cars2010`


- After the **Fuel Economy** data is loaded, combine three data sets into one data set. (Note: The name `dat` is very often used in these situations, `data` is a reserved R word.)  

```{r}
# Combines cars2010, cars2011 and cars2012 into one data set

dat <- dplyr::bind_rows(cars2010, cars2011, cars2012)    
```


- What is a good "naive guess" of FE? Show your work

```{r}
#we naively guess FE to be the mean of the observed fuel economy in dat 

naive_guess <- dat$FE %>% mean 
```


- plot FE (Fuel Econonomy) vs. EngDisp. Plot the naive guess.

```{r}
qplot(y = dat$FE, x =dat$EngDispl) +geom_hline(yintercept=naive_guess, color="red")
```

- Sample 10 observations from `dat`
- Plot this data. Add a line for the naive_guess. 


```{r}

set.seed(314) 

# Sample 
samp <- dat %>% sample_n(10) 

# Plots 
gg <- samp %>% ggplot(aes(x=EngDispl, y=FE))+geom_point(size=2.5)+scale_x_continuous(limits=c(0,10))

gg + geom_hline(yintercept=naive_guess, color="red")

```


## Exercise 2:


Write a loss functions for calculating:
- Root Mean Square Error
- Mean Absolute Error
- Median Absolute Error

All functions should accept two arguments: 


```{r}

rmse <- function(y,yhat){(y-yhat)^2 %>% mean %>% sqrt}

mae <- function(y, yhat) {(y-yhat) %>% abs %>% mean}

medae <- function(y, yhat) {(yhat - (y %>% median)) %>% median}

#the next set of instructions say to use the three functions to evaluate the loss/performance of the naive guess, but there is no obvious area in which to input that code, so I've included it here

rmse(dat$FE,naive_guess)

mae(dat$FE,naive_guess)

medae(dat$FE,naive_guess)

```

Use these functions to evaluate the loss/performance of:
- the naive guess



## Exercise 3: Linear Model and Model Performance 

- Use `lm` to create a linear model fitting the relationship between FE and EngDispl for the cars2010 data set


```{r}
fit.2010 <- lm(FE ~ EngDispl, data=cars2010) 
```

- Use your functions to evaluate the training error
- Use your model to:
-- predict the FE for 2011. What is the RMSE errors associated with the predictions.
-- predict the FE for 2012. What is the RMSE errors associated with the predictions.

```{r}

y.2010 <- fit.2010 %>% predict(cars2010)
y.2011 <- fit.2010 %>% predict(cars2011)
y.2012 <- fit.2010 %>% predict(cars2012)

rmse.2010 <- rmse(cars2010$FE, y.2010)
rmse.2011 <- rmse(cars2011$FE, y.2011)
rmse.2012 <- rmse(cars2012$FE, y.2012)

```


```{r}
# DO NOT EDIT 
rmse.2010 
rmse.2011
rmse.2012
```


## Exercise 4: 

- Model the fuel economy (`FE`) as a function of `EngDispl`, `NumCyl` and `VarValve` using the `cars2011` data set.  
- Provide betas


```{r}
#There wasn't a variable called VarValve; there was a VarValveTiming and a VarValveLift, so I just chose the first one.

fit.2010 <- lm(FE ~ EngDispl + NumCyl + VarValveTiming, data =cars2011)
betas <- coefficients(fit.2010)
```
